\begin{thebibliography}{15}
	
	\bibitem{sejarahtsel}
	\textbf{Sejarah Telkomsel}, Sejarah Telkomsel [Online]. Available: https://id.wikipedia.org/wiki/Telkomsel. [Accessed 17 March 2018].
	
	\bibitem{telkomsel}
	\textbf {Sejarah Telkomsel}, Sejarah Kami [Online]. Available: https://www.telkomsel.com/about-us/our-story/our-history. [Accessed 17 March 2018].
	
	\bibitem{aboutus}
	\textbf{Tentang Telkomsel}, Tentang Telkomsel [Online]. Available: https://www.telkomsel.com/about-us/our-story. [Accesed 17 March 2018].
	
	\bibitem{PHP}
	\textbf{PHP, "What is PHP?"} [Online]. Available: http://php.net/manual/en/intro-whatis.php. [Accessed 19 March 2018].		
	
	\bibitem{javascript}
	\textbf{What is JavaScript?}, Mozilla Developer Network. [Online]. Tersedia pada: https://developer.mozilla.org/en-US/docs/Learn/JavaScript/First\_steps/
	What\_is\_JavaScript. [Accessed 19 March 2018].
	
	\bibitem{laravel}
	\textbf{What is Laravel?}, Laravel (Project Using Symphony) [Online]. Available: https://symfony.com/projects/laravel. [Accessed 19 March 2018].
	
	\bibitem{apache}
	\textbf {Apache HTTP Server}, What is the Apache HTTP Server Project?, [Online]. Available: https://en.wikipedia.org/wiki/Apache\_HTTP\_Server. [Accessed 19 March 2018].
	
	\bibitem{mysql}
	\textbf{MySQL}, MySQL, [Online]. Available: http://www.oracle.com/technetwork/database/mysql/index.html. [Accessed 19 March 2018].
	
	\bibitem{ajax}
	\textbf{AJAX}, AJAX, [Online]. Available: https://id.wikipedia.org/wiki/AJAX. [Accessed 19 March 2018].
\end{thebibliography}
